### 2022-01-04 doc/src/VSLevel.tex
Add vstopei to CSR lists where forgotten
Additional virtual instruction traps when hvictl.VTI = 1

As introduced in Chapter~\ref{ch:CSRs}, several hypervisor and VS CSRs
are added:  \z{hvien}, \z{hvictl}, \z{hviprio1}, \z{hviprio2},
\z{vsiselect}, \z{vsireg}, \z{vstopi}, \z{vsseteipnum},
\z{vsclreipnum}, \z{vsseteienum}, and \z{vsclreienum}.
For RV32, the following ``high-half'' CSR partners are also added:
\z{hidelegh}, \z{hvienh}, \z{hviph}, \z{hviprio1h}, \z{hviprio2h},
\z{vsiph}, and \z{vsieh}.
As always, when executing in \mbox{VS-mode} or \mbox{VU-mode}, the
VS CSRs substitute for the corresponding supervisor CSRs.

@@

When \z{hstatus}.VGEIN is the valid number of a guest interrupt
file, values of \z{vsiselect} in the range \z{0x70}--\z{0xFF} select
registers of this guest interrupt file, just as values of \z{siselect}
in the same range select registers of the IMSIC's true supervisor-level
interrupt file.
The registers of an interrupt file that are accessed indirectly through
\z{vsiselect} and \z{vireg} are documented in Chapter~\ref{ch:IMSIC}
on the IMSIC, along with the effects of accessing CSRs \z{vsseteipnum},
\z{vsclreipnum}, \z{vsseteienum}, and \z{vsclreienum}.
Because all IMSIC interrupt files act identically, the guest interrupt
file that a virtual hart accesses through CSRs \z{siselect}, \z{sireg},
\z{sseteipnum}, \z{sclreipnum}, \z{sseteienum}, \z{sclreienum},
and \z{stopei} is indistinguishable from a true supervisor-level
interrupt file as seen from \mbox{S-mode} (or \mbox{HS-mode}).

@@

When bit VTI (Virtual Trap Interrupt control) =~1, attempts from
\mbox{VS-mode} to explictly access CSRs \z{sip}, \z{sie}, or, for RV32
only, \z{siph} or \z{sieh}, cause a virtual instruction exception.

>>>>

As introduced in Chapter~\ref{ch:CSRs}, several hypervisor and VS CSRs
are added:  \z{hvien}, \z{hvictl}, \z{hviprio1}, \z{hviprio2},
\z{vsiselect}, \z{vsireg}, \z{vstopi}, \z{vsseteipnum},
\z{vsclreipnum}, \z{vsseteienum}, \z{vsclreienum}, and \z{vstopei}.
For RV32, the following ``high-half'' CSR partners are also added:
\z{hidelegh}, \z{hvienh}, \z{hviph}, \z{hviprio1h}, \z{hviprio2h},
\z{vsiph}, and \z{vsieh}.
As always, when executing in \mbox{VS-mode} or \mbox{VU-mode}, the
VS CSRs substitute for the corresponding supervisor CSRs.

@@

When \z{hstatus}.VGEIN is the valid number of a guest interrupt
file, values of \z{vsiselect} in the range \z{0x70}--\z{0xFF} select
registers of this guest interrupt file, just as values of \z{siselect}
in the same range select registers of the IMSIC's true supervisor-level
interrupt file.
The registers of an interrupt file that are accessed indirectly through
\z{vsiselect} and \z{vireg} are documented in Chapter~\ref{ch:IMSIC}
on the IMSIC, along with the effects of accessing CSRs \z{vsseteipnum},
\z{vsclreipnum}, \z{vsseteienum}, \z{vsclreienum}, and \z{vstopei}.
Because all IMSIC interrupt files act identically, the guest interrupt
file that a virtual hart accesses through CSRs \z{siselect}, \z{sireg},
\z{sseteipnum}, \z{sclreipnum}, \z{sseteienum}, \z{sclreienum},
and \z{stopei} is indistinguishable from a true supervisor-level
interrupt file as seen from \mbox{S-mode} (or \mbox{HS-mode}).

@@

When bit VTI (Virtual Trap Interrupt control) =~1, attempts from
\mbox{VS-mode} to explictly access CSRs \z{sip}, \z{sie}, or, for RV32
only, \z{siph} or \z{sieh}, cause a virtual instruction exception.
Furthermore, when VTI =~1, a virtual instruction exception is raised
also for any attempt by the guest to write to a CSR that might
cause a bit of \z{vsip}/\z{vsiph} to change from one to zero,
excluding bit~9 for external interrupts (SEIP).
In particular, if register \z{vstimecmp} is implemented
(from extension Sstc), then attempts from \mbox{VS-mode}
to write to \z{stimecmp} or (RV32 only) \z{stimecmph}
cause a virtual instruction exception when VTI~=~1.

\begin{commentary}
For standard interrupt numbers in the range 13--63, and for
software interrupts (SSI), the corresponding interrupt-pending
bits in \z{vsip}/\z{vsiph} are defined as ``sticky,''
meaning a guest can clear them only by writing directly
to \z{sip}/\z{siph} (really \z{vsip}/\z{vsiph}).
Among the standard-defined interrupts, that leaves only
timer interrupts (STI), which can potentially be cleared
in \z{vsip} by writing a new value to \z{vstimecmp}.
\end{commentary}
